Response of soil microbiome composition to selection on methane oxidation rate

### 2023-06-23 manuscript/manuscript.Rmd
Add license
update figure captions

---
title: Artificial ecosystem selection reveals relationships between microbiome composition and ecosystem function
author: "Andrew H. Morris^1^* and Brendan J. M. Bohannan^1^"
output:
  word_document:
    reference_docx: reference.docx
bibliography: bibliography.bib
csl: vancouver.csl
---

@@

`r figures("response", paste0("Response to selection on soil CH~4~ oxidation rate. The y-axis is CH~4~ oxidation rate as the log~10~ of the additive inverse of the first-order exponential decay constant $k$ (i.e., $-k$) with units day^-1^ so that a more positive value represents a higher CH~4~ oxidation rate. Closed points are the positive selection treatment and open points are the control. The solid line is the regression for the positive selection treatment and the dotted line is the regression for the control. There was a significant difference of slopes between the positive selection treatment and the control (F~", compare_response_mods[[2,4]], ",", compare_response_mods[[2,2]], "~ = ", myround(compare_response_mods[[2,6]], 2), ", p = ", myround(compare_response_mods[[2,7]], 2), ")."))`

`r figures("beta", "Non-metric multidimensional scaling plot of beta diversity for all jars. Dissimilarities are rarefied Bray-Curtis dissimilarity averaged over 100 subsamples. Closed points are the positive selection treatment and open points are the control. Triangles are passage 2 and circles are passage 5.")`

>>>>

---
title: Response of soil microbiome composition to selection on methane oxidation rate
author: "Andrew H. Morris^1^* and Brendan J. M. Bohannan^1^"
output:
  word_document:
    reference_docx: reference.docx
bibliography: bibliography.bib
csl: vancouver.csl
---

@@

`r figures("response", paste0("Response to selection on soil CH~4~ oxidation rate. The y-axis is CH~4~ oxidation rate as the log~10~ of the additive inverse of the first-order exponential decay constant $k$ (i.e., $-k$) with units day^-1^ so that a more positive value represents a higher CH~4~ oxidation rate. Orange points and regression line are for the positive selection treatment and gray points and regression line are for the control. There was a significant difference of slopes between the positive selection treatment and the control (F~", compare_response_mods[[2,4]], ",", compare_response_mods[[2,2]], "~ = ", myround(compare_response_mods[[2,6]], 2), ", p = ", myround(compare_response_mods[[2,7]], 2), ")."))`

`r figures("beta", "Non-metric multidimensional scaling plot of beta diversity for all jars. Dissimilarities are rarefied Bray-Curtis dissimilarity averaged over 100 subsamples. Orange points are the positive selection treatment and gray points are the control. Circles are passage 2 and triangles are passage 5.")`
